Black hole mass function and its evolution -- the first prediction for the Einstein Telescope

### 2020-01-17 GW_BH_function/paper_draft/2020_revise/main_revised.tex
Push before combining Marek's edits

\newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
\newcommand{\blue}[1]{\textcolor{blue}{#1}} 
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

@@

\correspondingauthor{Xuheng Ding}
\email{dingxh@whu.edu.cn}

@@

\begin{abstract}
The knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe. We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BHMF and its evolution with redshift.  We perform the Monte Carlo simulation of the measurements of chirp signals from binary BH systems (BBH) that could be detected by ET, including the BH masses and their luminosity distances (\dl). We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$. Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests for three different sets of parameters and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$. Furthermore, assuming four sets of parameters, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ accurately at the uncertainty level of $\sim0.5$. Our numerical tests verify the reliability of our method; however, the uncertainty levels of the inferred parameters only applies for the assumed sets of the parameters which shouldn't be considered as a universal value for the general case.
}
\end{abstract}

@@

Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.  Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precison. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. 
In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities. Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}. Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift. In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET. We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.

This paper is organized as follows. In Section~\ref{sec_simulation} we describe the simulation of the BBH \textbf{inspiral} events detectable by ET using the Monte Carlo approach. In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data. In Section~\ref{sec_theory}, we introduce the theoretical framework to reconstruct the BHMFs, considering the noise realization and the selection effects. Furthermore, we make a further step by considering the power-law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section~\ref{sec_result}. The discussion and conclusions are given in the Section~\ref{sec_summary}. Throughout this paper, we assume a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector. Numerical predictions of BBH inspirals detectable by ET 
have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios\citep{Ola2013, Biesiada2014}}. More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog. The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study. We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.

@@

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity. ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) describe respectively the
direction to the BBH system relative to the detector and the binary orientation relative to the line of sight between it and the detector. 
They are independent and one can assume that $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$. The GW signal is considered as detectable if its \snr\ is over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

@@

We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system \textbf{as specified below. First key parameter is the redshift $z_s$.}  We sample the \textbf{merging BBH systems} according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
where the intrinsic BBH merger rate $\dot{n}_{0}(z_{s})$ is the one predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}, $\tilde{r}(z_{s})$ is the dimensionless comoving distance to the source, and $E (z_s)$ is
the dimensionless expansion rate of the universe at redshift $z_s$. 
%Note that the cosmological model we adopted is comply with the one in \citet{Dominik13}.
%For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is %fixed
\textbf{sampled from a uniform distribution} 
between $[M_{min}, m_1]$. Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF. 
\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}). We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system. We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.

Concerning the BHMF we consider two scenarios. In the first scenario, the exponent $\alpha$ is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET. In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
% \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{The above form is not motivated by any physical model.}
This is actually the first order Taylor expansion in the scale factor $a(t)$ for any function.

@@

\textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform. 
\blue{We note the fact that LIGO detections usually infer the properties an asymmetry upper and lower limit with ${\it skewed}$ possibility distributions. Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density as used to simulate the measured value} is:
 \begin{equation} \label{equ_lognorm}
P(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
 \end{equation}
\blue{We set up the standard errors for ${\cal M}_0$, \dl, and \mone\ by taking results by \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories. Note that the assumed uncertainty level of these properties should only affect the uncertainty (i.e., precision) of the inferred parameters, which wouldn't affect the validity (i.e., accuracy) test of our method.
}

@@

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{Illustration of the mock GW catalog} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
... & $...$ & ... & ... & ...\\
ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET. The reported values are the medians, with errors corresponding to the 16th and 84th percentiles.
}
\end{deluxetable}

>>>>

\newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
\newcommand{\blue}[1]{{#1}} 
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

@@

\correspondingauthor{{\bf Zong-Hong Zhu}}
\email{zhuzh@whu.edu.cn}

@@

\begin{abstract}
The knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe. We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BHMF and its evolution with redshift.  We perform the Monte Carlo simulation of the measurements of chirp signals from binary BH systems (BBH) that could be detected by ET, including the BH masses and their luminosity distances (\dl). We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$. Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we carried out the numerical tests and find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ with a precision of $\alpha\sim0.1$. Furthermore, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Taking a thousand of GW events and using \dl\ as the redshift estimator, our tests show that one could infer the value of evolving parameter $\alpha_1$ accurately with the uncertainty level of $\sim0.5$. Our numerical tests verify the reliability of our method. The uncertainty levels of the inferred parameters can be trusted directly for the several sets of the parameter we assumed, yet shouldn't be treated as a universal level for the general case.
\end{abstract}

@@

Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.  Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precision. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. 
In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities. Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of detecting $10^4-10^8$ coalescing BBHs per year \citep{Abernathy2011}. Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH inspiral events enable us to study the $\alpha$ as a function of redshift. In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH mergers that could be measured by the ET. We construct a mock BBH merger catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.

This paper is organized as follows. In Section~\ref{sec_simulation} we describe the simulation of the BBH inspiral events detectable by ET using the Monte Carlo approach. In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data. In Section~\ref{sec_theory}, we introduce the theoretical framework to reconstruct the BHMFs, considering the noise realization and the selection effects. Furthermore, we make a further step by considering the power-law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section~\ref{sec_result}. The discussion and conclusions are given in the Section~\ref{sec_summary}. Throughout this paper, we assume a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector. Numerical predictions of BBH inspirals detectable by ET 
have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios \citep{Ola2013, Biesiada2014}. More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog. The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH inspiral events with essential parameters that related to this study. We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.

@@

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective {\bf bandwidth. For simplicity, we follow the estimations by \citet{Taylor2012} and approximate $\zeta(f_{max})$ as  unity.} ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) describe respectively the
direction to the BBH system relative to the detector and the binary orientation relative to the line of sight between it and the detector. 
They are independent and one can assume that $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$. The GW signal is considered as detectable if its \snr\ is over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

@@

We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system as specified below. First key parameter is the redshift $z_s$.  We sample the merging BBH systems according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
where the intrinsic BBH merger rate $\dot{n}_{0}(z_{s})$ is the one predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}, $\tilde{r}(z_{s})$ is the dimensionless comoving distance to the source, and $E (z_s)$ is
the dimensionless expansion rate of the universe at redshift $z_s$. 
%Note that the cosmological model we adopted is comply with the one in \citet{Dominik13}.
%For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo\, is %fixed
sampled from a uniform distribution
between $[M_{min}, m_1]$. Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF. 
For the purpose of the simulation, however, all these parameters are necessary to determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}). We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH inspiraling system. We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.

Concerning the BHMF we consider two scenarios. In the first scenario, the exponent $\alpha$ is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET. In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
% \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably. Therefore the above ansatz is actually the first order Taylor expansion{, \bf assumption $\alpha$ as a function of the scale factor $a$, where $a(t) = \frac{1}{1+z}$.} 
%in the scale factor $a(t)$ applicable for any function.

@@

The quantities measurable from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$. Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform. 
Let us note that physical quantities inferred from the LIGO detections had asymmetric upper and lower uncertainty limits, hence they followed the  ${\it skewed}$  distributions. Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.
For instance, if the $m_{1,fid}$ is the true value for \mone, the probability density used to simulate the measured value is:
 \begin{equation} \label{equ_lognorm}
P(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
 \end{equation}
We set up the uncertainties for ${\cal M}_0$, \dl, and \mone\ by taking results of \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories. Note that the assumed uncertainty level of these quantities only affect the uncertainty of the inferred parameters (i.e. the precision) and wouldn't affect the validity test of our method (i.e. the  accuracy).

@@

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{Illustration of the mock GW catalog} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $8.14\substack{+1.80\\-1.48}$  & $25356.8\substack{+5614.1\\-4596.4}$  & $9.91\substack{+2.19\\-1.80}$ & 18.512 \\
ID2 & $43.93\substack{+9.73\\-7.96}$  & $12956.9\substack{+2868.7\\-2348.7}$  & $28.64\substack{+6.34\\-5.19}$ & 46.953 \\
ID3 & $5.05\substack{+1.12\\-0.92}$  & $8617.6\substack{+1908.0\\-1562.1}$  & $3.60\substack{+0.80\\-0.65}$ & 9.836 \\
ID4 & $13.93\substack{+3.08\\-2.53}$  & $47473.1\substack{+10510.7\\-8605.4}$  & $10.97\substack{+2.43\\-1.99}$ & 17.563 \\
ID5 & $11.37\substack{+2.52\\-2.06}$  & $21485.0\substack{+4756.8\\-3894.6}$  & $10.68\substack{+2.36\\-1.94}$ & 31.107 \\
ID6 & $21.67\substack{+4.80\\-3.93}$  & $9446.1\substack{+2091.4\\-1712.3}$  & $7.64\substack{+1.69\\-1.39}$ & 31.624 \\
ID7 & $32.20\substack{+7.13\\-5.84}$  & $69317.4\substack{+15347.1\\-12565.1}$  & $19.35\substack{+4.28\\-3.51}$ & 13.496 \\
ID8 & $7.73\substack{+1.71\\-1.40}$  & $25104.5\substack{+5558.2\\-4550.7}$  & $6.68\substack{+1.48\\-1.21}$ & 9.612 \\
ID9 & $35.63\substack{+7.89\\-6.46}$  & $16321.8\substack{+3613.7\\-2958.6}$  & $10.96\substack{+2.43\\-1.99}$ & 16.202 \\
ID10 & $18.78\substack{+4.16\\-3.40}$  & $54375.1\substack{+12038.8\\-9856.5}$  & $15.16\substack{+3.36\\-2.75}$ & 29.232 \\
... & $...$ & ... & ... & ...\\
ID991 & $29.40\substack{+6.51\\-5.33}$  & $40765.1\substack{+9025.5\\-7389.5}$  & $29.79\substack{+6.59\\-5.40}$ & 28.134 \\
ID992 & $6.41\substack{+1.42\\-1.16}$  & $16026.7\substack{+3548.4\\-2905.2}$  & $4.54\substack{+1.01\\-0.82}$ & 17.550 \\
ID993 & $10.27\substack{+2.27\\-1.86}$  & $33207.9\substack{+7352.3\\-6019.6}$  & $8.57\substack{+1.90\\-1.55}$ & 8.037 \\
ID994 & $21.26\substack{+4.71\\-3.85}$  & $56088.6\substack{+12418.2\\-10167.1}$  & $16.01\substack{+3.54\\-2.90}$ & 19.871 \\
ID995 & $14.35\substack{+3.18\\-2.60}$  & $29022.0\substack{+6425.6\\-5260.8}$  & $13.50\substack{+2.99\\-2.45}$ & 14.230 \\
ID996 & $22.50\substack{+4.98\\-4.08}$  & $49038.7\substack{+10857.3\\-8889.2}$  & $18.48\substack{+4.09\\-3.35}$ & 11.636 \\
ID997 & $5.42\substack{+1.20\\-0.98}$  & $23537.5\substack{+5211.3\\-4266.6}$  & $4.54\substack{+1.01\\-0.82}$ & 12.562 \\
ID998 & $25.07\substack{+5.55\\-4.55}$  & $19555.4\substack{+4329.6\\-3544.8}$  & $18.81\substack{+4.16\\-3.41}$ & 17.846 \\
ID999 & $5.70\substack{+1.26\\-1.03}$  & $24024.9\substack{+5319.2\\-4355.0}$  & $3.61\substack{+0.80\\-0.65}$ & 23.020 \\
ID1000 & $39.23\substack{+8.69\\-7.11}$  & $31835.1\substack{+7048.4\\-5770.7}$  & $22.31\substack{+4.94\\-4.04}$ & 15.884 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET. The reported values are the medians, with errors corresponding to the 16th and 84th percentiles, assuming $\alpha=1.6$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$. Note that this mock data is re-simulated every time in each realization}.
\end{deluxetable}

\vspace{1cm}
\section{Theoretical Framework}  \label{sec_theory}
In this section, we describe the fitting procedure for the parameterized BHMFs. 
In principle, the modeling for a dataset which follows a power-law distribution as Equation~(\ref{equ_powlaw}) is very straightforward. To derive the posterior of the parameters, one only needs to combine all the measured median values together in a joint likelihood:
 \begin{equation} \label{equ_lik_powlaw}
 P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min})
 \end{equation}
 where $m_{1,i}$ is the primary mass inferred from the $i$~-~$th$ GW event.
However, the median values of simulated \mone, as shown in Table~\ref{tab_GW_mock_data}, actually deviate from the initial power-law distribution. This deviation stems from several effects that exist in reality. In Section~\ref{sec_likelihood_noise} and \ref{sec_likelihood_sf}, we introduce them and explore the ways to account for them.
